---
title: "MAPS Sync"
output: html_document
---
This document is a meta script to run all cleaning and analysis scripts on MAPS data after data is collected.

#Step 1: Gathering Data
After participant leaves, data must be gathered off of all devices and put onto the MAPS1 harddrive and the Box.

**Put all original data into a folder named Raw**

1) Webcamera Video: Let the video finish loading and then run through handbrake for a mp3 format of the video on the secondary laptop.
2) Log: Grab out of MAPS-data folder on main laptop
3) Eyetracker: Grab out of MAPS-data folder on main laptop
4) Main Computer Audio: Grab out of MAPS-data folder on main laptop
5) Accelerometer Data: Export from Consensys and grab from either main laptop or accelerometer computer

#Step 2: Find sync times
MAPS was started in several different ways when protocol was still being established.

Sync Types:
1) *1-2-3-4 Touch*: Examiner touched the screen as they said the numbers 1 through 4 aloud. This was supposed to give us a specific timepoint in the webcam audio to match to the touch in the sesison log. (Used in MAPS-002 - MAPS-011)

2) *Double Audio*: Webcamera and main laptop collected audio at the same time. The accelerometer sync button was pushed in the first 30 seconds of the session to give both audios a distinct audio to line up. Time points are found using Audacity (goal: use an R script to find beep start times)

3) *Manual*: If there was an error in the script, the main laptop did not record audio. Manual sync times were found an used in sync script. 

**Add sync times to file: (/Box Sync/MAPS/Data/Sync/sync_timestamps.csv)**

#Step 3: Clean Data

Define computer and participant ID for following scripts
```{r define_id_computer}
#enter child ID
id <- "MAPS-003"

# enter location- servername
username <- "myerju"
```


##Eyetracker:

How to annotate eyetracker files (from Joel Adams):
 1. Delete the contents of "MAPS-alignment/data/annotations" on your local machine if you have new annotations to add
 2. Move all of the eyetracker.csv files and log.tsv files to MAPS-alignment/data/logs on your local machine
 3. If there are any differences in the MAPS-alignment script, git pull
 4. Open up terminal and run  `ssh joel`
 4. Run ready scripts in "/home/adamjo/MAPS-annotation/scripts/output_scripts"
 5. Verify that this generates an appropriate file in "/home/adamjo/annotations"
      - they should have their original (weird) formatting and end with .csv like "Charli's Crafty Kitchen_short.mov.csv"
 6. On local machine, cd to MAPS-alignment/data/annotations
 7. scp joel:/home/adamjo/MAPS-annotation/scripts/output_scripts/*.csv .
      - dot at the end of the command means “secure copy all of the csvs from joel at the path /…/…/output_scripts and put them in current directory
 8. Run 'python align_annotation.py util.py' on local machine

##CERT: 

Step 1: Merge log file and eyetracker csv

```{r eyetracker_log_merge}
source('/Users/myerju/Box Sync/MAPS/Scripts/Meta MAPS/log_eyetracker_sync.R')
```

Step 2: Pre-CERT Video Split Timestamps

```{r pre_cert_timestamps}
source('/Users/myerju/Box Sync/MAPS/Scripts/Meta MAPS/Pre-CERT_video_split.R')
```

Step 3: Split Video using python

open up the terminal and run 

`cd../..
 cd Volumes/MAPS1/Participant\ Recordings
 jupyter notebook
`

This will open up that folder in jupyter notebook. Choose emotions_split and run the script on your id numbers.
``{python}
import re, os, subprocess, csv

ids = ['005']
for id in ids:
    movpath = 'MAPS-' + id + '/raw/MAPS-' + id + '.mp4'
    csvpath = 'MAPS-' + id + '/CERT/MAPS-' + id + '_emotions_timepoints.csv'
    output = 'MAPS-' + id + '/CERT/MAPS-' + id + '_emotions.mp4'
    with open(csvpath, 'rt') as f:
        reader = csv.reader(f)
        for row in reader:
            start_time = row[1]
            duration = row[3]
subprocess.check_call(["ffmpeg", "-ss", start_time, "-t", duration, "-i", movpath, "-vcodec", "copy", "-acodec", "copy", output])
``

Step 4: Run Video through CERT
Now that you have your cut video in the CERT folder, you can open up CERT and run it through the system. When it is done processing (it may take a long time), save the txt file in your CERT analysis folder on the harddrive.

```{r pre_cert_timestamps}
source('/Users/myerju/Box Sync/MAPS/Scripts/Meta MAPS/Post-CERT_cleanup.R')
```

Note: 2 warning messages will appear about "numerical expression has 2 elements: only the first used". This is a good thing. Don't worry about it :)



