---
title: "MAPS Analyses"
output: html_document
---

We will be doing a series of analyses for the upcoming R01 for MAPS. Some of them can be done without the markup (pre-markup analyses)

```{r import_load_packages}
pkgs <- c("dplyr", "tidyr", "ggplot2", "psych", "fuzzyjoin") # list packages needed
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
suppressMessages(ipak(pkgs)) # take function, and give it that list
```

###PRE-MARKUP ANALYSES

1) amount of data missing from eyetracker data 
  - we will need to merge log file and eyetracker csv (use fuzzyjoin package by David Robinson)
  - make sure to section out eye tracker data in between calibration and storytelling task


###Statistics using REDCap information

```{r import_csv}
#on julianne's laptop 
#eyetracker <- (read.csv("/Users/julianne/Desktop/Raw-selected/MAPS-003_eyetracker.csv", header=TRUE)) 

#log <-  (read.csv("/Users/julianne/Desktop/Raw-selected/MAPS-003_log.csv", header=TRUE))

#on julianne's boxsync
eyetracker <- (read.csv("/Users/myerju/Box Sync/MAPS/Data/MAPS-003_eyetracker.csv", header=TRUE)) 

log <- (read.csv("/Users/myerju/Box Sync/MAPS/Data/MAPS-003_log.csv", header=TRUE)) 
```  

Tidy our log data for Joining later
```{r, tidy_data}
log_nodesc <- log[-(1:3), ] #get rid of extra 10.4 timestamp entries at beginning - no descriptions at top

log_touch <- log_nodesc %>%   # create dataframe with timestamp and touchquadrant
  filter(event == "touchquadrant") %>%
  select(timestamp, entry) 

colnames(log_touch)[2] <- "touchquadrant" #rename event column for join later

log_nodesc <- filter(log_nodesc, !grepl('touchquadrant', event)) #get rid of multiple touchscreen rows

log_nodesc <- left_join(log_nodesc, log_touch, by="timestamp") #join for a column that represents the touchquadrant
```

We can't use the difference join with two factors because it cannot subtract one from the other. They must be numeric. The current structure of the Timestamp column is MM:SS.MS. We can use "period to seconds" in lubridate to create a new joining column we will call timestamp_ sec. 

```{r fix_timestamp}
#create new vectors of timestamp_sec for log_nodesc
log_timestamp_sec <- (as.numeric(as.POSIXct(strptime(log_nodesc$timestamp, format = "%M:%OS"))) - 
    as.numeric(as.POSIXct(strptime("0", format = "%S"))))

#create new vectors of timestamp_sec for eyetracker
eyetracker_timestamp_sec <- (as.numeric(as.POSIXct(strptime(eyetracker$timestamp, format = "%H:%M:%OS"))) - 
    as.numeric(as.POSIXct(strptime("0", format = "%S"))))

#Create a new column for join in log_nodesc and eyetracker
log_nodesc <- log_nodesc%>%
  mutate(timestamp_sec = log_timestamp_sec)

eyetracker <- eyetracker%>%
  mutate(timestamp_sec = eyetracker_timestamp_sec)
```

```{r, join_output}
sync_data <- difference_left_join(eyetracker, log_nodesc, by = "timestamp_sec", max_dist =.5)
```


2) Session completion rates

```{r session_complete}
maps_complete <- maps %>% 
  filter(session_complete==1)
```

3) Participation rates for storytelling task

```{r story_complete}
maps_complete %>%
  summarise(storytell_complete)
```

4) Session duration statistics

```{r session_duration}
maps_complete %>%
  mean(session_time)
```

5) Parent Feedback 
  - how many kids enjoyed their time in maps
```{r session_like}
maps_complete %>%
  summarize(like_overall)
```

  - how many kids previously watched youtube
```{r session_like}
maps_complete %>%
  summarize(youtube_child)
```

  - how often kids watch youtube
```{r session_like}
maps_complete %>%
  summarize(youtube_frequency)
```
