---
title: "MAPS Analyses"
output: html_document
---

We will be doing a series of analyses for the upcoming R01 for MAPS. Some of them can be done without the markup (pre-markup analyses)

#PRE-MARKUP ANALYSES

##Amount of data missing from eyetracker data 
  - we will need to use merged log and eyetracker data (_see "log_eyetracker_sync.Rmd"" for more info_)
  - make sure to section out eye tracker data in between calibration and storytelling task

###Load Packages
```{r import_load_packages}
pkgs <- c("dplyr", "tidyr", "ggplot2", "psych", "fuzzyjoin", "zoo", "readr") # list packages needed
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
suppressMessages(ipak(pkgs)) # take function, and give it that list
```

###Load in synced data
**MAKE SURE TO REPLACE MAPS ID WITH CORRECT NUMBER USING FIND AND REPLACE ALL FOR FULL SCRIPT TO WORK**
```{r import_csv}
#on MAPS1 Hard drive
sync_data_postcalib <- (read_csv("/Volumes/MAPS1/Participant Recordings/MAPS-002/synced/MAPS-002_postcalib_data_sync.csv"))
```

###Missing eyetracker data per participant

How do we want to define missing data?

both right and left eye = true missing data points
How often they are looking at the screen? How often the eyetracker is working?
Per stimulus? Stimulus type?
Group difference?
```{r separate_data}
right_eye <- sync_data_postcalib %>%
  select(contains("right"))

left_eye <- sync_data_postcalib %>%
  select(contains("left"))
```

```{r data_missing_ind}
#amount of data missing from x and y coordinates in RIGHT eye
right_gaze_0 <- right_eye %>%
  count(right_gaze_x_px == 0.00 & right_gaze_y_px == 0.00) %>%
  mutate(prop_right_gaze = prop.table(n)) 

#amount of data prop from eye position in RIGHT eye
right_position_0 <- right_eye %>%
  count(right_eye_position_x_mm== 0.00 & right_eye_position_y_mm == 0.00 & right_eye_position_z_mm == 0.00) %>%
  mutate(prop_right_position = prop.table(n)) 

#amount of data prop from pupil diameter in RIGHT eye
right_diameter_0 <- right_eye %>%
  count(right_pupil_diameter_mm == 0.00)%>%
  mutate(prop_right_size= prop.table(n)) 

#amount of data prop from x and y coordinates in LEFT eye
left_gaze_0 <- left_eye %>%
  count(left_gaze_x_px == 0.00 & left_gaze_y_px == 0.00) %>%
  mutate(prop_left_gaze = prop.table(n)) 

#amount of data prop from eye position in LEFT eye
left_position_0 <- left_eye %>%
  count(left_eye_position_x_mm== 0.00 & left_eye_position_y_mm == 0.00 & left_eye_position_z_mm == 0.00) %>%
  mutate(prop_left_position = prop.table(n)) 

#amount of data prop from pupil diameter in LEFT eye
left_diameter_0 <- left_eye %>%
  count(left_pupil_diameter_mm == 0.00)%>%
  mutate(prop_left_size = prop.table(n)) 

#amount of data prop from x and y coordinates in BOTH eyes
both_gaze_0 <- sync_data_postcalib %>%
  count(right_gaze_x_px == 0.00 & right_gaze_y_px == 0.00 & left_gaze_x_px == 0.00 & left_gaze_y_px == 0.00) %>%
  mutate(prop_both_gaze = prop.table(n)) 

#amount of data prop from eye position in BOTH eyes
both_position_0 <- sync_data_postcalib %>%
  count(right_eye_position_x_mm== 0.00 & right_eye_position_y_mm == 0.00 & right_eye_position_z_mm == 0.00 & left_eye_position_x_mm== 0.00 & left_eye_position_y_mm == 0.00 & left_eye_position_z_mm == 0.00) %>%
  mutate(prop_both_position = prop.table(n)) 

#amount of data prop from pupil diameter in BOTH eyes
both_diameter_0 <- sync_data_postcalib %>%
  count(right_pupil_diameter_mm == 0.00 & left_pupil_diameter_mm == 0.00)%>%
  mutate(prop_both_size = prop.table(n)) 


#add first column of data type
data_type <- c("present data", "missing data")

#create a table with all stats from above
missing_eyetracker <- cbind(data_type, right_gaze_0, right_position_0, right_diameter_0, left_gaze_0, left_position_0, left_diameter_0, both_gaze_0, both_position_0, both_diameter_0)

#rename to specify what n describes
colnames(missing_eyetracker) <- c("data_type", "1right_gaze_x_px == 0 & right_gaze_y_p...", "n_right_gaze", "prop_right_gaze", "2right_eye_position_x_mm == 0 & right_...", "n_right_position", "prop_right_position", "3right_pupil_diameter_mm == 0", "n_right_size", "prop_right_size", "left_gaze_x_px == 0 & left_gaze_y_px ...", "n_left_gaze", "prop_left_gaze", "left_eye_position_x_mm == 0 & left_ey...", "n_left_position", "prop_left_position", "left_pupil_diameter_mm == 0", "n_left_size", "prop_left_size", "4right_gaze_x_px == 0 & right_gaze_y_p...", "n_both_gaze", "prop_both_gaze", "5right_eye_position_x_mm == 0 & right_...", "n_both_position", "prop_both_position", "6right_pupil_diameter_mm == 0 & left_p...", "n_both_size", "prop_both_size")                          
#get rid of unneccesary identifier columns
missing_eyetracker <- missing_eyetracker %>%
  select(-contains("== 0"))
```

```{r export_missing_data_ind}
write.csv(missing_eyetracker, file = "/Volumes/MAPS1/Participant Recordings/MAPS-002/synced/MAPS-002_missing_eyetracker.csv")
```

###Total missing data
```{r import_csv}
#on MAPS1 Hard drive
missing_eyetracker_002 <- (read_csv("/Volumes/MAPS1/Participant Recordings/MAPS-002/synced/MAPS-002_missing_eyetracker.csv"))
missing_eyetracker_018 <- (read_csv("/Volumes/MAPS1/Participant Recordings/MAPS-018/synced/MAPS-018_missing_eyetracker.csv"))
```

```{r total_data}

```



#Statistics using REDCap information

##Session completion rates

```{r session_complete}
maps_complete <- maps %>% 
  filter(session_complete==1)
```

##Participation rates for storytelling task

```{r story_complete}
maps_complete %>%
  summarise(storytell_complete)
```

##Session duration statistics
move to eyetracker analysis
```{r session_duration}
maps_complete %>%
  mean(session_time)
```

#Statistics from Parent Feedback 

##How many kids enjoyed their time in maps?
```{r session_like}
maps_complete %>%
  summarize(like_overall)
```

##How many kids previously watched youtube?
```{r session_like}
maps_complete %>%
  summarize(youtube_child)
```

##How often kids watch youtube?
```{r session_like}
maps_complete %>%
  summarize(youtube_frequency)
```
