---
title: "sync_output"
output: html_document
---
MAPS has 4 kinds of output data:

1) Log file: text file, timestamps for beginning and end of each video, touchscreen timestamps and locations, and pause, skip, or repeats - synced with eyetracker csv

2) Eyetracker: csv file, timestamps synced with log file

3) Webcam video: .wmv file, includes audio file, collected on separate computer

4) Accelerometer: csv file, data logged to internal chip, has button that creates a spike in data and audible beep to sync audio and data

5) Audio file: *added 7/7/16*, wav file, starts simultaneously with the session so it is synced with log file and eyetracker file, records accelerometer beep for full syncronisation

#SYNCING WEBCAMERA AND STIMULUS PRESENTATION LOG

##Method 1: Touchscreen and examiner voice
The first 10 participants were recorded with touchscreen tap and the examiner saying the numbers "one" through "four". The timestamps for the spoken numbers were found manually by opening the webcam videos in audacity. 

###Load Packages
```{r import_load_packages}
pkgs <- c("dplyr", "tidyr", "readr", "lubridate") # list packages needed
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
suppressMessages(ipak(pkgs)) # take function, and give it that list
```

###Import Data
```{r define_id}
#enter child ID - eventually mega script will define this
id <- "MAPS-015"

sync_type1 <- c("MAPS-001", "MAPS-002", "MAPS-003", "MAPS-004", "MAPS-005", "MAPS-006", "MAPS-007", "MAPS-008", "MAPS-009", "MAPS-010", "MAPS-011")

#on julianne's computer 
username <- "myerju"

#on julianne's laptop 
#username <- "julianne"
```

```{r import_data}
#import data
log <-  read_tsv(paste("", "Volumes", "MAPS1", "Participant Recordings", id, "raw", paste(id,"_log.tsv", sep = ""), sep = "/"))
video_sync <- read.csv(paste("", "Users", username, "Box Sync", "MAPS", "Data", "Sync", "sync_timestamps.csv", sep = "/"), header = T) #csv of manually recorded timestamps
```

We will create a column that gives the difference between the log timestamp and the webcam timestamp.
```{r video_diff}
if (id %in% sync_type1) {
  video_sync <- mutate(video_sync, vid_diff = one_time_sec - touch_time_sec)
} else {
  video_sync <- mutate(video_sync, vid_diff = webcam_beep_start_sec - maincomp_beep_start_sec)
}
```

There are a few where the session started before the webcamera so if the difference is < 0, the difference will be subtracted from the timestamp and if the difference is > 0, the difference will be added to the timestamp.
```{r adjust_sync}
#create an ID column in log
log <- log %>%
  mutate(ID = id)

#make ID a character type
video_sync$ID <- as.character(video_sync$ID)

#left join by ID number
log_sync <- left_join(log, video_sync, by = c("ID"))

#create new vectors of timestamp_sec for log_nodesc and eyetracker
log_timestamp_sec <- (as.numeric(as.POSIXct(strptime(log$timestamp, format = "%H:%M:%OS"))) -
    as.numeric(as.POSIXct(strptime("0", format = "%S"))))

#Create a new column for join 
log_sync <- log_sync%>%
  mutate(timestamp_sec = log_timestamp_sec)

#mutate a new column based on if difference is positive or negative
log_sync <- mutate(log_sync, webcam_timestamp_sec = 
                     ifelse(vid_diff > 0, timestamp_sec + vid_diff, 
                            timestamp_sec - abs(vid_diff)))

#fix the format for a column in format HH:MM:SS.msec
webcam_timestamp <- format(.POSIXct(log_sync$webcam_timestamp_sec), "%M:%OS")
webcam_timestamp <- paste0("00:", webcam_timestamp)

log_sync <- log_sync %>%
  mutate(webcam_timestamp = webcam_timestamp)
```

```{r delete_extra_col}
extra <- c("ID", "one_time", "one_time_sec", "touch_time", "touch_time_sec", "webcam_beep", "maincomp_beep", "notes")

log_sync <- log_sync[, !names(log_sync) %in% extra]
```


##Export Synced Log file
```{r export_csv}
write.csv(log_sync, file =paste("", "Volumes", "MAPS1", "Participant Recordings", id, "synced", paste(id,"_log_webcam_sync.csv", sep = ""), sep = "/")) 
```


##Method 2: Aligning beeps
For the audio syncing, we are starting with a script written by Kevin Sheng (ksheng7746@gmail.com) in 2015.

```{r import_load_packages}
pkgs <- c("tuneR", "signal", "seewave", "dpylr", "tidyr") # list packages needed
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
suppressMessages(ipak(pkgs)) # take function, and give it that list
```

```{r read_audio}
main_audio <- readWave(paste("", "Volumes", "MAPS1", "Participant Recordings", id, "raw", paste(id,".wav", sep = ""), sep = "/"), from=0, to= Inf, units = "seconds")
```

```{r audio_plot}
min_count <- sum(main_audio@left)/60


main_audio_beg <- main_audio %>%
  main_audio@samp.rate

afilter(main_audio@left, main_audio@samp.rate, plot = T, listen = F, output = "matrix")
```


```{r sampling_rate}
samp_rate <- 44100  #audio sampling rate
shimmer_samp_rate <- 50
block_size <- round(samplingRate / shimmerSamplingRate) #gives number of audio samples for every shimmer sample
```


NEED TO CONVERT:

[y,Fs] = audioread('aug_18_beep.mp3','native'); #make an array of y = aug..., x= native?
x=double(y(:,2));   #Read columns 1-2 of all rows in y; double returns the double-precision value for X

t=linspace(0,length(y)/Fs,length(y));
figure;plot(t,x);xlabel('time (s)');ylabel('Amplitude'); title('Audio signal') # plot audio signal


Sampling Rate for syncronizing Shimmers?

```{r original_script}
goertzel <- function(samples){          #Single bin Fourier Transform, returns magnitude of signal at target frequency for block of samples
  N <- 200                              #FFT Points
  k <- round(0.5 + (N * targetFrequency / samplingRate))
  w <- (2 * pi * k) / N
  cosine <- cos(w)
  sine <- sin(w)
  coeff <- 2 * cosine
  Q0 <- 0
  Q1 <- 0
  Q2 <- 0
  
  for(i in seq(1, dim(array(samples)), 1))
  {
    Q0 <- coeff * Q1 - Q2 + samples[i]
    Q2 <- Q1
    Q1 <- Q0
  }
  
  #   Re <- (Q1 - Q2 * cosine)            
  #   Im <- (Q2 * sine)
  #   magnitude <- Re^2 + Im^2
  magnitude <- sqrt(Q1^2 + Q2^2 - Q1 * Q2 * coeff)          #optimized Goertzel for magnitude only
  scale <- log(magnitude)
  Q0 <- 0
  Q1 <- 0
  Q2 <- 0
  return(scale)
}
```


```{r}
hann <- function(samples){              #Windowing
  windowed <- numeric()
  for(i in seq(1, dim(array(samples)), 1)){
    windowed[i] <- .5 * (1 - cos(2 * pi * i / dim(array(samples)))) * samples[i]
  }
  return(windowed)
}
```


```{r audio_peak}
#Get the peak from audio signal (look for 4175Hz signal)

readAudio <- function(){
  
  magnitude <- numeric(size / blockSize)      #Pre-allocate arrays to improve performance
  timer <- numeric(size / blockSize)
  beep <- 0
  j <- 1
  
  for(i in seq(1, block_size, length(x)-block_size)){          #Perform Goertzel on block of samples, results in "Goertzeled" sampling rate equal to Shimmer sampling rate
    magnitude[j] <- goertzel(hann(samples[i:(i + blockSize - 1)]))  
    timer[j] <- i / samplingRate 
    j <- j + 1
  }
  plot(magnitude, type = "l")
  # audioData <- data.frame(timer, magnitude)
  # plot(audioData, type = "l")        
  return(magnitude)
}
```

j=1;
for i=1:blockSize:length(x)-blockSize 
x1=x(i:(i+blockSize-1));
N=length(x1);
[maxValue,indexMax] = max(abs(fft(x1-mean(x1))));
if ~isempty(indexMax)
f=4175;
freq_indices = round(f/Fs*N) + 1;
mag(j)=abs(goertzel(x1,freq_indices));
else
  mag(j)=0;
end
j=j+1;
end

[S1,I1] = max(mag);%% search for the peak
t1=t(1:blockSize:length(x)-blockSize); %% time scale for the samples version of audio
disp(['Beep detected ' num2str(t1(I1)),' seconds after video was started']);

audio=zeros(length(mag),1);
audio(I1)=1;%% single peak representing beep in audio signal 

figure; %% plot single peak representations
plot(t1,audio);title('audio time');xlabel('time (s)');






```{r}
parseShimmerData <- function(){
  header <- scan("C:/Users/Kevin/Desktop/ShimmerData.csv", skip = 3, nlines = 1, sep = ",", what = character())         #Too many header lines
  data <- read.csv("C:/Users/Kevin/Desktop/ShimmerData.csv", skip = 4, header = FALSE)
  names(data) <- header
  data[,c(1,3,5:9)] <- list(NULL)
  for(i in seq(1, nrow(data), 1)){                      #ccf() can give errors for unchanging series
    if(data$mVolts[i] == 0){
      data$mVolts[i] <- sample(0:1, 1)
    }
  }
  # data$mSecs <- data$mSecs - data$mSecs[1]            #Shimmer3 timestamp does not begin when recording starts, but when data collection starts
  # plot(data$mVolts, type = "l")
  return(data$mVolts)
}

maxCCF<- function(a,b)                  #Use cross correlation to find lag
{
  d <- ccf(a, b, plot = TRUE, na.action = na.pass, lag.max = size / blockSize)
  cor = d$acf
  lag = d$lag
  res = data.frame(cor,lag)
  res_max = lag[which.max(res$cor)]
  return(res_max)
} 

offset <- round(maxCCF(parseShimmerData(), readAudio()) / shimmerSamplingRate, 3)

if(offset < 0){
  print(paste0("The microphone began recording ", abs(offset), " seconds before the Shimmer3" ))
}else{
  print(paste0("The microphone began recording ", abs(offset), " seconds after the Shimmer3" ))
}

```



JULIANNE'S ATTEMPT AT AUDIO SYNC

```{r import_data}
audio <- readWave("/Users/julianne/Desktop/MAPS-016.wav", from = 0, to = Inf, units = "minutes") #replace with correct path
```

```{r}
main_audio <- readWave("/Users/julianne/Desktop/MAPS-016.wav", from = 0, to = 10, units = "second") #first minute of main computer's audio

webcam_audio <- readWave("/Users/julianne/Desktop/MAPS-016.wav", from = 0, to = Inf, units = "minutes") 
```

```{r amplitude_graph}
timeArray <- (0:(960000-1)) / main_audio@samp.rate
timeArray <- timeArray * 1000 #scale to milliseconds

s1 <- main_audio@left

plot(timeArray, s1, type='l', col='black', xlab='Time (ms)', ylab='Amplitude') 
```

```{r afilter}
afilter(s1, main_audio@samp.rate, threshold = 50, plot = TRUE, listen = FALSE, output = "matrix")

ffilter(s1, main_audio@samp.rate, from = 4000, to = 4200, bandpass = TRUE, custom = NULL, wl = 1024, ovlp = 75, wn = "hanning", fftw = FALSE, output="matrix")

4100
```

