---
title: "CERT Single Plot"
output: html_document
---

```{r import_load_packages, include=FALSE}
pkgs <- c("dplyr", "tidyr", "ggplot2", "psych", "readxl", "readr") # list packages needed
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
suppressMessages(ipak(pkgs)) # take function, and give it that list
```

Make sure to do a Find and Replace All command to replace the dataframe name for the whole code to work.

```{r set_working directory}
#setting our wd up here will make importing data less wordy

#MARISSA'S LAPTOP
#setwd("/Users/Marissa Renda/Documents/Senior Fall 2016/PSY499 - Senior Thesis/CERT/cert_stim")

#JULIANNE'S DESKTOP
#setwd("/Users/myerju/Box Sync/MAPS/Data/CERT/Marissa-Yawn")

#JULIANNE'S LAPTOP
#setwd("/Users/julianne/Box Sync/MAPS/Data/CERT/Marissa-Yawn")

```

```{r import_data}
##CSV FILE
cert_stim_4 <- read_csv("cert_stim_4_clean.csv")
```

#Single AU plot
If you want to look at any particular AU, then here is the code for just one line plot.

*Note:* Future analysis- Align the peaks of yawn AUs (start with jaw drop). We will need to add a second layer with new dataframe source or combine the two if we want to facet the AUs.
        1. Start with 2 yawns from same person and then move on to yawns from 2 different people
        2. Find peak by using `max()`, subtract difference and create graph with aligned peaks
```{r plot_1_au}
au<- ggplot(cert_stim_4, aes(x=frame, y=au_26_jaw_drop))
au<- au+ geom_line()
#au<- au+ geom_smooth()  #uncomment if you want smoothed graph
au<- au+ ggtitle("Jaw Drop (AU26)")
au
```


**FOR MARISSA TO DO: Add a plot that has multiple observations on it using this example (http://stackoverflow.com/questions/19921842/plotting-multiple-time-series-on-the-same-plot-using-ggplot)**


